A Question on the Efficiency of Transit in Absurd Situations

### 2019-01-03 public/post/2019-01-02-transit.Rmd

---
title: Transit
author: Effi Feldblum
date: '2019-01-02'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

@@

```{r echo=FALSE, out.width = '100%', eval = FALSE}
knitr::include_graphics("google_maps_whats_here.png")

```
```{r echo=FALSE, out.width = '35%', eval = FALSE}
knitr::include_graphics("Untitled.png")
```

@@

```{r echo=FALSE, out.width = '50%',eval = FALSE}
knitr::include_graphics("Septa_logo.png")

@@

```{r echo=FALSE, out.width = '25%',eval = FALSE}
knitr::include_graphics("mta_logo.png")

@@

```{r echo=FALSE, out.width = '25%', eval = FALSE}
knitr::include_graphics("wmata_logo.png")

>>>>

---
title: A Question on the Efficiency of Transit in Absurd Situations
author: Effi Feldblum
date: '2018-08-22'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

---

@@

```{r echo=FALSE, out.width = '100%'}

img1_path <- "data/transit/x2.png"
include_graphics(img1_path)
```

```{r echo=FALSE, out.width = '35%'}

img2_path <- "data/transit/Untitled.png"
include_graphics(img2_path)
```

@@

```{r echo=FALSE, out.width = '50%'}

img3_path <- "data/transit/Septa_logo.png"
include_graphics(img3_path)

@@

```{r echo=FALSE, out.width = '25%'}

img4_path <- "data/transit/mta_logo.png"
include_graphics(img4_path)

@@

```{r echo=FALSE, out.width = '25%'}

img5_path <- "data/transit/wmata_logo.png"
include_graphics(img5_path)
